Model-based pretreatment for regression with correlated variables.

### 2014-04-10 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@524 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

When one wants to explain a phenomenon based on some covariates, the first statistical method tried frequently is the linear regression. It provides a predictive model with a good interpretability even  for non-statistician and is simple to learn. Therefore, linear regression is used in nearly all the fields where statistics are made \cite{montgomery2012introduction}, from industry and astronomy \cite{isobe1990linear} to sociology \cite{longford2012revision}.
Linear regression is a very classic situation but sometimes it has to face an also classical problem: the variance of the estimators. We note the linear regression model:
\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the  $n\times 1$ response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I_n})$ the noise of the regression, with $\boldsymbol{I_n}$ the $n$-sized identity matrix and $\sigma_Y >0$. The $p\times 1$ vector $\boldsymbol{\beta}$ is the vector of the coefficients of the regression, that can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{OLS}). %As shown in section \ref{sectionOLS}, 
	Estimation of $\boldsymbol{\beta}$ requires the inversion of $\boldsymbol{X}'\boldsymbol{X}$ which will be ill-conditioned or even singular if some covariates depend linearly from each other. 
Variance of $\boldsymbol{\hat\beta}$ increases based on two aspects :
\begin{itemize}
	\item The dimension $p$ (number of covariates) of the model: the more covariates you have the greater variance you get.
	\item The correlations within the covariates: strongly correlated covariates give bad-conditioning and increase variance of the estimators .
\end{itemize}

	With the rise of informatic, datasets contains more and more covariates and thus more and more useless covariates. So dimension reduction becomes a necessity. Moreover, when you use more covariates, you increase the chance to have correlated ones. It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results or even no results at all. Prediction and interpretation are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favored to improve the process instead of only predict defects.
		~\\	~\\

%bibliographie	
	Because \textsc{OLS} is the minimum-variance unbiased estimator, penalized methods try to reduce the variance introducing some bias to improve the bias-variance trade-off and get better prediction.
Moreover, real datasets imply many irrelevant variables so we have to use variable selection methods.

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq k
	\end{equation}
	But Ridge regression do not aim at selecting covariates because coefficients tends to 0 but don't reach 0.
	So it gives difficult interpretations for large values of $p$.

	The Least Absolute Shrinkage and Selection Operator (\textsc{LASSO} \cite{tibshirani1996regression}) consists in a shrinkage of the regression coefficients based on a $\lambda$ parametric $L_1$ penalty to obtain zeros in $\hat{\boldsymbol{\beta}}$:
		\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\boldsymbol{\beta} \parallel_1\leq \lambda
		\end{equation}	
	 The Least Angle Regression (\textsc{LAR} \cite{efron2004least}) Algorithm offers a very efficient way to obtain the whole LASSO path and is very attractive. It requires only the same order of magnitude of computational effort as \textsc{OLS} applied to the full set of covariates. And it  really selects covariates with coefficients set exactly to 0.
	 But \textsc{LASSO} also faces consistency problems \cite{Zhao2006MSC} when confronted  with correlated covariates. 
%	 Another limitation of the \textsc{LASSO} is that it preserves at most $n$ predictors (troublesome when in high dimension). 
	 Some recent variants of the \textsc{LASSO} does exist for the choice of the penalization coefficient like the adaptative \textsc{LASSO} \cite{zou2006adaptive} or the random \textsc{LASSO} \cite{wang2011random}.
	 \\

	Elastic net\cite{zou2005regularization}	is a method developed to be a compromise between Ridge regression and the \textsc{LASSO}. 
%	Given data set $(Y,X)$ and two parameters $(\lambda_1,\lamda_2)$, define artificial data set $(Y^*,X^*)$ by :
%	\begin{equation}
%		X^*_{(n+p)\times p}=(1+\lambda_2)^{-1/2}\left( X  \sqrt{\lambda_2}I \right), \ \ \  Y^*_{(n+p)}=\left( Y 0 \right)
%\end{equation}		
	Elastic net can be written:
	\begin{equation}
		\boldsymbol{\hat{\beta}}=(1+\lambda_2) \operatorname{argmin}\left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta} \parallel_2^2 \right\rbrace, \textrm{ subject to } (1-\alpha)\parallel\boldsymbol{\beta}\parallel_1+\alpha\parallel\boldsymbol{\beta}\parallel_2^2\leq t \textrm{ for some } t
	\end{equation}
	where $\alpha=\frac{\lambda_2}{(\lambda_1+\lambda_2)}$. 
	%It seems to give good predictions. 
	But it is based on the grouping effect so correlated covariates get similar coefficients and are selected together whereas LASSO will choose between one of them and will then obtain same predictions with a more parsimonious model.
	\\

@@

	But it requires to suppose having many covariates with the same level of effect on the response variable and seems to stay less efficient in prediction than elastic net. Spike and Slab variable selection \cite{ishwaran2005spike} also relies on Gaussian mixture (the spike and the slab) hypothesis for the $\beta_j$ and gives a subset of covariates (not grouped) on which to compute \textsc{OLS} but has no specific protection against correlations issues.
	~\\	~\\
% Principe de la méthode

 Where some reduce the dimension without looking at correlations and then have to suppose having no correlations between the remaining covariates,  we propose to focus on the correlations, giving a marginal model with orthogonal covariates and an explicit structure between covariates. Our work is based on the assumption that if we know explicitly the source of correlations, we could use this knowledge to avoid the problem.
 In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other tools for dimension reduction and estimation without suffering from correlations. Practically speaking we use a system of linear regressions between the covariates to model the structure of the correlations. This structure is obtained by a MCMC algorithm optimizing the penalized likelihood of the joint law on the dataset $\boldsymbol{X}$. This algorithm is part of the R package \textsc{CorReg} accessible on \textsc{CRAN}. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

 	%plan
 	This paper will first present the marginal regression model and its properties before describing in Section 3 the random walk used to find the structure.
 	We will then look at some numerical results on simulated (Section \ref{sectionsimul}) and real industrial datasets (Section \ref{sectionrealcase}) before concluding and giving some perspectives in the last part.

\section{Model to select decorrelated covariates}
\subsection{A classical problem: correlations in regression}\label{sectionOLS}
For a model defined by 
	\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X\beta} + \boldsymbol{\varepsilon}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I_n})$ with $\boldsymbol{I_n}$ the $n$-sized identity matrix,
	we have the following Ordinary Least Squares (\textsc{OLS}) estimator:
	\begin{equation}
		\boldsymbol{\hat{\beta}}=\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}\boldsymbol{X}'\boldsymbol{Y}
	\end{equation}
	With variance matrix
	\begin{equation}
		\operatorname{Var}(\boldsymbol{\hat{\beta}})=\sigma_Y^2\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1} \label{eqOLS}
	\end{equation}
	and without any bias.
	When correlations between covariates are strong, the matrix to invert is ill-conditioned and the variance explodes.
	Another problem is that matricial inversion requires $n\geq p$. When it is not the case, a frequently used alternative is the Moore-Penrose generalized inverse \cite{katsikis2008fast}. In the followings, matrices inverses when $n<p$ will refer to this generalized inverse. Thus OLS can obtain some results even with $n<p$ (see section \ref{sectionsimul} ).
\subsection{Our proposal: modelisation of the correlations}
Let now $\boldsymbol{X} \in \mathcal{R}^{n\times p}$ be a set of $p$ correlated covariates.
We propose to explicitly define a family of $p_2$ internal regressions between covariates with $I_2$ the set of indices of endogenous variables in $\boldsymbol{X}$ (explained ones) and $I_1=\{I_1^1,\dots,I_1^p \}$ the set of the sets of indices of exogenous covariates (explaining ones) with $\forall j \notin I_2, I_1^j=\emptyset$. Then we have an explicit structure $S=(I_1,I_2,p_1,p_2)$ where $\boldsymbol{p_1}=(p_1^1,\dots,p_1^{p_2})$ is the vector of the number of covariates in each internal regression. Thus we have $p_2=|I_2|$ and $p_1^j=|I_1^j|$ where $|.|$ represents the cardinal of an ensemble.

In the following, we note $\boldsymbol{X^j}$ the $j^{th}$ column of a matrix $\boldsymbol{X}$.
For lighter notation we define $\boldsymbol{X_2}=\boldsymbol{X^{I_2}}$ the matrix of the endogenous covariates and $\boldsymbol{X_1}=\boldsymbol{X}\setminus \boldsymbol{X_2}$ the matrix of the remaining exogenous covariates.

The family of $p_2$ regressions within correlated covariates in $\boldsymbol{X}$ is noted:
	\begin{equation}
		\boldsymbol{X_2}_{|\boldsymbol{X_1},S} \textrm{ defined by }\forall j \in I_2: \boldsymbol{X^j}_{|\boldsymbol{X_1},S}=\boldsymbol{X_1\alpha_j}+\boldsymbol{\varepsilon_j} \textrm{ with } \boldsymbol{\varepsilon_j} \sim(\boldsymbol{0},\sigma^2_j\boldsymbol{I_n}) \label{SR}
	\end{equation}
		where $\boldsymbol{\delta_j} \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_1^j$).

We make the hypothesis of the uncrossing rule $I_1\cap I_2=\emptyset$ {\it i.e.} endogenous variables don't explain other covariates, thus we have a partition $\boldsymbol{X}=\left[\boldsymbol{X_1},\boldsymbol{X_2}\right]$.

The discrete structure $S$ is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(\boldsymbol{X},\boldsymbol{Y})$, the residuals ($\boldsymbol{\varepsilon_j}$) would not stay Gaussian (see the appendices).

@@

The structure obtained gives a system of linear regression that can be viewed as a recursive Simultaneous Equation Model (\textsc{SEM})\cite{davidson1993estimation}. Such a system is easy to interpret but estimation don't take advantage of the explicit structure \cite{TIMM} when the structure is straight forward (recursive \textsc{SEM}).
  	Some methods take into account correlations but they only consider covariances between residuals \textsc{SUR} (Seemingly Unrelated Regression \cite{SURzellner}) or  endogenous variables like \textsc{SPRING} (Structured selection of Primordial Relationships IN the General linear model \cite{chiquetconf}). 
  	\\ Here we suppose independency between the residuals but in other cases it remains the possibility to use such methods to estimate the $\boldsymbol{\delta_j}$ and $\sigma_j$.

	  We make the choice to distinguish the response variable from the other endogenous variables (that are on the left of a regression). Thus we have one regression on our response variable and a system of sub-regressions (without the response variable). Then we consider correlations between the explicative covariates of the main regression, not between the residuals.

@@

\subsection{A by-product model: marginal regression with decorrelated covariates}
 The structure is supposed to be the source of the correlations and allows us to define a marginal regression model based on a reduced set of independent covariates without significant information loss. So we may obtain two kinds of zeros in the marginal model : coerced zeros due to correlations (redundant information) and estimated ones with classical variable selection methods applied on remaining variables. This two kinds of zero won't be interpreted in the same way and thus consistency issues don't mean interpretation issues any more. So we dodge the drawbacks of both grouping effect and variable selection.
 	\\
Let $\boldsymbol{Y} \in \mathcal{R}^n$ be a response variable we want to explain with $\boldsymbol{X}$:
	\begin{equation}
			\boldsymbol{Y}_{|\boldsymbol{X_1},\boldsymbol{X_2},S}=\boldsymbol{X_1\beta_1}+\boldsymbol{X_2\beta_2}+\boldsymbol{\varepsilon_Y} \textrm{ with } \boldsymbol{\varepsilon_Y} \sim \mathcal{N}(\boldsymbol{0},\sigma^2_Y\boldsymbol{I_n});	\label{MainR}
		\end{equation}
		where $\boldsymbol{\beta}=(\boldsymbol{\beta_1},\boldsymbol{\beta_2}) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $\boldsymbol{I_n}$ the identity matrix. 
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $\boldsymbol{X_2}$ a marginal regression model on $\boldsymbol{Y}$ {\it depending only on uncorrelated covariates $\boldsymbol{X_1}$}:
\begin{eqnarray}
	\boldsymbol{Y}_{|\boldsymbol{X_1},S}&=&\boldsymbol{X_1} (\boldsymbol{\beta_{1}}+ \sum_{j \in I_2}\beta_{j}\boldsymbol{\alpha_j})+  \sum_{j \in I_2}\beta_{j}\boldsymbol{\varepsilon_{j}}+\boldsymbol{\varepsilon_Y} \label{Trueexpl} \\
	&=&\boldsymbol{X_1}\boldsymbol{\beta_1^*}+\boldsymbol{\varepsilon_Y^*}=\boldsymbol{X}\boldsymbol{\beta^*}+\boldsymbol{\varepsilon_Y^*} \textrm{ where }\boldsymbol{\beta^*}=(\boldsymbol{\beta_1^*},\boldsymbol{\beta_2^*}) \textrm{ and } \boldsymbol{\beta_2^*}=\boldsymbol{0}
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It is a variable pre-selection independent of the response $\boldsymbol{Y}$.

\subsection{Strategy of use: pretreatment before classical selection methods}\label{interpretation}
As a pretreatment, it allows usage of any method in a second time to estimate $\alpha$like LASSO or even stepwise \cite{seber2012linear}.

@@

After selection and estimation we will obtain a model with { \it two kinds of zeros}: those from decorrelating step and those from selection step, with different meanings. 
Thus consistency issues don't mean interpretation issues any more. So we dodge the drawbacks of both grouping effect and variable selection.

Each equation here is very simple (only linear regressions). 
Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable (no cycles and no chain-effect) and straightforward readable.

>>>>

When one wants to explain a phenomenon based on some covariates, the first statistical method tried frequently is the linear regression. It provides a predictive model with a good interpretability even  for non-statistician and is simple to learn. Therefore, linear regression is used in nearly all the fields where statistics are made \cite{montgomery2012introduction}, from industry and astronomy \cite{isobe1990linear} to sociology \cite{longford2012revision}.
Linear regression is a very classic situation but sometimes it has to face an also classical problem: the variance of the estimators. We note the linear regression model:
\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the  $n\times 1$ response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I}_n)$ the noise of the regression, with $\boldsymbol{I}_n$ the $n$-sized identity matrix and $\sigma_Y >0$. The $p\times 1$ vector $\boldsymbol{\beta}$ is the vector of the coefficients of the regression, that can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{OLS}). %As shown in section \ref{sectionOLS}, 
	Estimation of $\boldsymbol{\beta}$ requires the inversion of $\boldsymbol{X}'\boldsymbol{X}$ which will be ill-conditioned or even singular if some covariates depend linearly from each other. 
Conditionning of $\boldsymbol{X}'\boldsymbol{X}$ get worse based on two aspects : the dimension $p$ (number of covariates) of the model (the more covariates you have the greater variance you get)
	 and the correlations within the covariates: strongly correlated covariates give bad-conditioning and increase variance of the estimators .

	With the rise of informatics, datasets contain more and more covariates and thus dimension reduction becomes a necessity. Moreover, increasing the number of covariates also increases the chance to have correlated ones. It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favored to improve the process instead of only predict defects, so robust estimation is needed.
		~\\	~\\

%bibliographie	
	Because \textsc{OLS} is the minimum-variance linear unbiased estimator, penalized methods try to reduce the variance introducing some bias to improve the bias-variance trade-off and get better prediction.

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \lambda \textrm{ with } \lambda>0
	\end{equation}
	But Ridge regression do not aim at selecting covariates because coefficients tends to 0 but don't reach 0.
	So it gives difficult interpretations for large values of $p$.	
	Moreover, real datasets imply many irrelevant variables so we have to use variable selection methods.

	The Least Absolute Shrinkage and Selection Operator (\textsc{LASSO} \cite{tibshirani1996regression}) consists in a shrinkage of the regression coefficients based on a $\lambda$ parametric $L_1$ penalty to obtain zeros in $\hat{\boldsymbol{\beta}}$:
		\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\boldsymbol{\beta} \parallel_1\leq \lambda \textrm{ with } \lambda>0
		\end{equation}	
	 The Least Angle Regression (\textsc{LAR} \cite{efron2004least}) Algorithm offers a very efficient way to obtain the whole LASSO path and is very attractive. It requires only the same order of magnitude of computational effort as \textsc{OLS} applied to the full set of covariates. And it  really selects covariates with coefficients set exactly to 0.

%	 Another limitation of the \textsc{LASSO} is that it preserves at most $n$ predictors (troublesome when in high dimension). 
	 Some recent variants of the \textsc{LASSO} do exist for the choice of the penalization coefficient like the adaptative \textsc{LASSO} \cite{zou2006adaptive} or the random \textsc{LASSO} \cite{wang2011random}.
	 \\

	Elastic net\cite{zou2005regularization}	is a method developed to be a compromise between Ridge regression and the \textsc{LASSO}. 
%	Given data set $(Y,X)$ and two parameters $(\lambda_1,\lamda_2)$, define artificial data set $(Y^*,X^*)$ by :
%	\begin{equation}
%		X^*_{(n+p)\times p}=(1+\lambda_2)^{-1/2}\left( X  \sqrt{\lambda_2}I \right), \ \ \  Y^*_{(n+p)}=\left( Y 0 \right)
%\end{equation}		
	Elastic net can be written:
	\begin{equation}
		\boldsymbol{\hat{\beta}}=(1+\lambda_2) \operatorname{argmin}\left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta} \parallel_2^2 \right\rbrace, \textrm{ subject to } (1-\alpha)\parallel\boldsymbol{\beta}\parallel_1+\alpha\parallel\boldsymbol{\beta}\parallel_2^2\leq t \textrm{ for some } t
	\end{equation}
	where $\alpha=\frac{\lambda_2}{(\lambda_1+\lambda_2)}$. 
	%It seems to give good predictions. 
	But it is based on the grouping effect so correlated covariates get similar coefficients and are selected together whereas LASSO will choose between one of them and will then obtain same predictions with a more parsimonious model. Hence interpretations are not the same and nothing explains why. So it can be very confusing. 
	\\

@@

	But it requires to suppose having many covariates with the same level of effect on the response variable and seems to stay less efficient in prediction than elastic net. Spike and Slab variable selection \cite{ishwaran2005spike} also relies on Gaussian mixture (the spike and the slab) hypothesis for the $\beta_j$ and gives a subset of covariates (not grouped) on which to compute \textsc{OLS} but has no specific protection against correlations issues.
	 \textsc{LASSO} also faces consistency problems \cite{Zhao2006MSC} when confronted  with correlated covariates and we see that none of the above methods take the correlations into account.

	~\\	~\\
% Principe de la méthode

 Where some reduce the dimension without looking at correlations,  we propose to focus on the correlations, giving an explicit structure between covariates that helps to define a marginal model with uncorrelated covariates. Thus we have variable selection with explanation and improve interpretation and not only prediction.
 Our work is based on the assumption that if we know explicitly the source of correlations, we could use this knowledge to avoid the problem.
 In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other tools for dimension reduction and estimation without suffering from correlations. Practically speaking we use a system of linear regressions between the covariates to model the structure of the correlations. This structure is obtained by a MCMC algorithm optimizing the penalized likelihood of the joint law on the dataset $\boldsymbol{X}$. This algorithm is part of the R package \textsc{CorReg} accessible on \textsc{CRAN}. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

 	%plan
 	This paper will first present the marginal regression model and its properties before describing in Section 3 the random walk used to find the structure.
 	We will then look at some numerical results on simulated (Section \ref{sectionsimul}) and real industrial datasets (Section \ref{sectionrealcase}) before concluding and giving some perspectives in Section \ref{conclusion}.

\section{Model to select decorrelated covariates}
\subsection{A classical problem: correlations in regression}\label{sectionOLS}
For a model defined by 
	\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X\beta} + \boldsymbol{\varepsilon}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I_n})$ with $\boldsymbol{I_n}$ the $n$-sized identity matrix,
	we have the following Ordinary Least Squares (\textsc{OLS}) estimator:
	\begin{equation}
		\boldsymbol{\hat{\beta}}=\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1}\boldsymbol{X}'\boldsymbol{Y}
	\end{equation}
	With variance matrix
	\begin{equation}
		\operatorname{Var}(\boldsymbol{\hat{\beta}})=\sigma_Y^2\left(\boldsymbol{X}'\boldsymbol{X} \right) ^{-1} \label{eqOLS}
	\end{equation}
	and without any bias.
	When correlations between covariates are strong, the matrix to invert is ill-conditioned and the variance increases, giving unstable and unusable estimator \cite{hoerl1970ridge}.
	Another problem is that matricial inversion requires $n\geq p$. 
\subsection{Our proposal: modelisation of the correlations}
Let now $\boldsymbol{X} \in \mathcal{R}^{n\times p}$ be a set of $p$ correlated covariates.
In the following, we note $\boldsymbol{X^j}$ the $j^{th}$ column of a matrix $\boldsymbol{X}$.

We propose to explicitly define a family of $p_r$ internal regressions between covariates with $I_r$ the set of indices of endogenous variables in $\boldsymbol{X}$ (explained ones). We note $\boldsymbol{X}_r=\boldsymbol{X}^{I_r}$ the sub-matrix of the redundant covariates (explained by others) and  $\boldsymbol{X}_f$ the remaining submatrix of free covariates (independent explaining covariates).
We focus here on the expression of $P(\boldsymbol{X}_r|\boldsymbol{X}_f)$.

We have $I_f=\{I_f^1,\dots,I_f^p \}$ the set of the sets of indices of exogenous covariates (explaining ones $=\boldsymbol{X}_f$) with $\forall j \notin I_r, I_f^j=\emptyset$. Then we have an explicit structure $S=(I_f,I_r,p_f,p_r)$ where $\boldsymbol{p_f}=(p_f^1,\dots,p_f^{p_r})$ is the vector of the number of covariates in each internal regression. Thus we have $p_r=|I_r|$ and $p_f^j=|I_f^j|$ where $|.|$ represents the cardinal of an ensemble.

The family of $p_r$ regressions within correlated covariates in $\boldsymbol{X}$ is noted:
	\begin{equation}
		\boldsymbol{X}_{r|\boldsymbol{X}_f,S} \textrm{ defined by }\forall j \in I_r: \boldsymbol{X}^j_{|\boldsymbol{X}_f,S}=\boldsymbol{X}_f\boldsymbol{\alpha}_j+\boldsymbol{\varepsilon}_j \textrm{ with } \boldsymbol{\varepsilon}_j \sim(\boldsymbol{0},\sigma^2_j\boldsymbol{I}_n) \label{SR}
	\end{equation}
		where $\boldsymbol{\alpha}_j \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_f^j$).

We make the hypothesis of the uncrossing rule $I_f\cap I_r=\emptyset$ {\it i.e.} endogenous variables don't explain other covariates, thus $\boldsymbol{X}_f$ and $\boldsymbol{X}_f$ give a partition of $\boldsymbol{X}$, so $\boldsymbol{X}_f=\boldsymbol{X}\setminus \boldsymbol{X}_r$.
The discrete structure $S$ is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(\boldsymbol{X},\boldsymbol{Y})$, the residuals ($\boldsymbol{\varepsilon}_j$) would not stay Gaussian (see the appendices).

@@

The structure obtained gives a system of linear regression that can be viewed as a recursive Simultaneous Equation Model (\textsc{SEM})\cite{davidson1993estimation}. Such a system is easy to interpret but estimation don't take advantage of the explicit structure \cite{TIMM} when the structure is straight forward (recursive \textsc{SEM}).
  	Some methods take into account correlations but they only consider covariances between residuals \textsc{SUR} (Seemingly Unrelated Regression \cite{SURzellner}) or  endogenous variables like \textsc{SPRING} (Structured selection of Primordial Relationships IN the General linear model \cite{chiquetconf}) without explicit expression of the correlations and thus a smaller interpretation potential.
  	\\ Here we suppose independency between the residuals but in other cases it remains the possibility to use such methods to estimate the $\boldsymbol{\alpha}_j$ and $\sigma_j$.

	  We make the choice to distinguish the response variable from the other endogenous variables (that are on the left of a regression). Thus we have one regression on our response variable ($P(\boldsymbol{Y}|\boldsymbol{X})$ and a system of sub-regressions (without the response variable: $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)$). Then we consider correlations between the explicative covariates of the main regression, not between the residuals.

@@

\subsection{A by-product model: marginal regression with decorrelated covariates}
Now we know $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)$ by the structure of sub-regressions, we are able to define a marginal regression model $P(\boldsymbol{Y}|\boldsymbol{X}_f,S)$ based on the reduced set of independent covariates $\boldsymbol{X}_f$ without significant information loss. 
 	\\
Let $\boldsymbol{Y} \in \mathcal{R}^n$ be a response variable we want to explain with $\boldsymbol{X}=[\boldsymbol{X}_f,\boldsymbol{X}_r]$:
	\begin{equation}
			\boldsymbol{Y}_{|\boldsymbol{X}_f,\boldsymbol{X}_r,S}=\boldsymbol{X}_f\boldsymbol{\beta}_f+\boldsymbol{X}_r\boldsymbol{\beta}_r+\boldsymbol{\varepsilon_Y} \textrm{ with } \boldsymbol{\varepsilon_Y} \sim \mathcal{N}(\boldsymbol{0},\sigma^2_Y\boldsymbol{I}_n);	\label{MainR}
		\end{equation}
		where $\boldsymbol{\beta}=(\boldsymbol{\beta}_f,\boldsymbol{\beta}_r) \in  \mathcal{R}^p$ is the vector of the regression coefficients associated respectively to $\boldsymbol{X}_f$ and $\boldsymbol{I}_n$ the identity matrix. 
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $\boldsymbol{X}_r$ a marginal regression model on $\boldsymbol{Y}$ {\it depending only on uncorrelated covariates $\boldsymbol{X}_f$}:
\begin{eqnarray}
	\boldsymbol{Y}_{|\boldsymbol{X}_f,S}&=&\boldsymbol{X}_f (\boldsymbol{\beta}_f+ \sum_{j \in I_r}\beta_{j}\boldsymbol{\alpha}_j)+  \sum_{j \in I_r}\beta_{j}\boldsymbol{\varepsilon}_j+\boldsymbol{\varepsilon}_Y \label{Trueexpl} \\
	&=&\boldsymbol{X}_f\boldsymbol{\beta}_f^*+\boldsymbol{\varepsilon}_Y^*=\boldsymbol{X}\boldsymbol{\beta}^*+\boldsymbol{\varepsilon}_Y^* \textrm{ where }\boldsymbol{\beta}^*=(\boldsymbol{\beta}_f^*,\boldsymbol{\beta}_2^*) \textrm{ and } \hat{\boldsymbol{\beta}}_r^*=\boldsymbol{\beta}_r^*=\boldsymbol{0}
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It is a variable pre-selection independent of the response $\boldsymbol{Y}$.

\subsection{Strategy of use: pretreatment before classical selection methods}\label{interpretation}
As a pretreatment, it allows usage of any method in a second time to estimate $\boldsymbol{\beta}^*$, even with variable selection methods like LASSO or even stepwise \cite{seber2012linear}.

After selection and estimation we will obtain a model with { \it two steps of variable selection}: the decorrelation step (coerced zeros associated to redundant information) and the classical selection step, with different meanings for obtained zeros in $\hat{\boldsymbol{\beta}}^*$. 
 This two kinds of zero won't be interpreted in the same way and thus consistency issues don't mean interpretation issues any more. So we dodge the drawbacks of both grouping effect and variable selection.

@@

Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable (no cycles and no chain-effect) and straightforward readable.
